Resistive magneto-rotational instability in massive protoplanetary disks

### 2013-11-12 paper/results.tex
paper update, begun results section

\subsection{Reference cases}
%ideal, non sg

%ideal, sg

%non ideal smooth, non sg

%non ideal struct. non sg

%non ideal smooth, sg

%non ideal struc, sg

%grav instab.

>>>>

\subsection{MRI in self-gravitating polytropic disks with uniform
  resistivity}  
We first calculate the MRI as a function of $Q$ in a polytropic disk
with uniform resistivity ($A=1$). Here, we consider $Q\in[0.2,4]$,
corresponding to stronly self-gravitating to non-self-gravitating
disks, for mid-plane Elsasser numbers $\Lambda_0\in[0.3,10]$. We fix $k_x=0.1$ and 
$\beta=100$.

It is useful to first see how self-gravity may still play a role even
though density and potential perturbations are expected to be
negligible because $k_x\ll1$, i.e. the linear response is
non-self-gravitating. 
%even though the linear response is expected to be incompressible
%because $k_x\ll 1$, i.e. non-self-gravitating. 
\cite{sano99} found that the MRI wavelength, normalized by $H$, can be estimated as
\begin{align}
  \lambda=\mathrm{max}\left(\lambda_\mathrm{ideal},\lambda_\mathrm{resis}\right), 
\end{align}
where
\begin{align}
  \lambda_\mathrm{ideal} = f v_A = \frac{f}{\sqrt{\beta\rho}} 
\end{align}
is the ideal MRI wavelength, and 
\begin{align}
  \lambda_\mathrm{resis} =\frac{\eta}{f v_A}=\frac{f}{\Lambda_0}\sqrt{\frac{\rho}{\beta}}
\end{align}
is the MRI wavelength in the limit of high resistivity.

\subsection{Resistive MRI in massive polytropic disks with layered
  resistivity}

\subsection{GI in magnetized isothermal disks with uniform
  resistivity}

\subsection{GI in magnetized isothermal disks with layered
  resistivity}

### 2013-11-12 paper/setup.tex
paper update, begun results section

Example resistivity profiles are shown in Fig. \ref{eqm_resis} for the isothermal disk. 
The midplane Elsasser number is $\Lambda(0)=0.1$ and the conductivity is boosted by a factor $A=10$ 
from the midplane to the upper disk boundary. The figure compares a strongly self-gravitating case
($Q=0.2$) and the non-self-gravitating limit ($Q=10$).

@@

\subsection{System parameters}
The strength of self-gravity is parametrized by
\begin{align}
  Q \equiv \frac{\Omega^2}{4\pi G\rho_0}
\end{align}
\citep{mamat10}. The plasma $\beta$ measures the inverse strength of
the magnetic field,
\begin{align}
  \beta \equiv \frac{\csmid^2}{v_{A0}^2} =
  \frac{\csmid^2\mu_0\rho_0}{B^2},  
\end{align}
where $v_{A0}$ is the midplane Alfven speed. The strength of
resistivity is measured by the midplane Elsasser number 
\begin{align}
  \Lambda \equiv \frac{v_{A0}^2}{\eta_0\Omega} = \frac{f^2 R_m}{\beta}, 
\end{align}
where the second equality defines the magnetic Reynolds number $R_m$
and $f\equiv \csmid/H\Omega$ is a numerical factor of order unity.

>>>>

Example resistivity profiles are shown in Fig. \ref{eqm_resis} for the isothermal disk. 
The conductivity is boosted by a factor $A=10$ from the midplane to
the upper disk boundary. The figure compares a strongly self-gravitating case
($Q=0.2$) and the non-self-gravitating limit ($Q=10$).

@@

\subsection{System parameters}
The strength of self-gravity is parametrized by
\begin{align}
  Q \equiv \frac{\Omega^2}{4\pi G\rho_0}
\end{align}
\citep{mamat10}. The plasma $\beta$ measures the inverse strength of
the magnetic field,
\begin{align}
  \beta \equiv \frac{\csmid^2}{v_{A0}^2} =
  \frac{\csmid^2\mu_0\rho_0}{B^2},  
\end{align}
where $v_{A0}$ is the midplane Alfven speed. The strength of
resistivity is measured by the midplane Elsasser number 
\begin{align}
  \Lambda_0 \equiv \frac{v_{A0}^2}{\eta_0\Omega} = \frac{f^2 R_m}{\beta}, 
\end{align}
where the second equality defines the magnetic Reynolds number $R_m$
and $f\equiv \csmid/H\Omega$ is a numerical factor of order unity.
The Elsasser number as a function of height is $\Lambda(z)\equiv
v_A^2/\eta\Omega$.
